\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage[hang,small,margin=1in]{caption}
\usepackage{titlesec}
\usepackage[authoryear,colon,sort&compress]{natbib}

\renewcommand{\headrulewidth}{0pt}
\fancyfoot{}
\fancyfoot[C]{\sffamily Page \thepage\ of \pageref{LastPage}}
\pagestyle{fancy}

\titleformat{\section}{\bfseries\MakeUppercase}{\arabic{\thesection}}{1em}{}
\titleformat{\subsection}{\bfseries}{\arabic{\thesection}.\arabic{\thesubsection}}{1em}{}
\titleformat{\subsubsection}{\itshape}{\arabic{\thesection}.\arabic{\thesubsection}.\arabic{\thesubsubsection}}{1em}{}

\setlength{\parindent}{0cm}
\setlength{\parskip}{1em}

\captionsetup[figure]{labelfont=it, font=it}
\captionsetup[table]{labelfont={it,sc}, font={it,sc}}

\hypersetup{colorlinks, linkcolor = black, citecolor = black, urlcolor = black}
\urlstyle{same}


\begin{document}

Soo-Hyun Yoo \\
930-569-466 \\
GEO 300, F12 \\
Sandra Huynh \\
Energize Corvallis due 5/15/15

\section*{Energize Corvallis}

\subsection*{Pre-assessment}

Sustainability has always at least been at the back of my mind, but getting
things done has always come before everything else (i.e., if I need the heat up
in order to concentrate, then so be it). That said, my mother is particularly
conscious of water and energy use in the house, and I have picked up some of
her habits over the years -- turning off unused appliances, using task
lighting, air-drying laundry, and recycling.

I had also already completed an Energize Corvallis challenge in October 2014
with the goals of tuning up my car, receiving free lights and aerators, biking,
and turning off lights. These were things I had already been planning to do
more of, and I was fairly successful with them. I particularly enjoyed tuning
up my car as I spend my free time tinkering anyway.

Some of the tasks this second time around, namely matching pans to element
sizes and washing full loads, were not things I had thought about before.

\subsection*{Analysis}

I picked the following actions:

\begin{enumerate}
  \item Turn your heater down
  \item Turn off your computer, TVs, radios or games that use electricity when
    you're not using them
  \item Use Task Lighting
  \item Match Pan to Element Size
  \item Wash Full Loads
\end{enumerate}

I picked the first three which I had already been doing 80 percent of the time
and sounded easy to do if I remembered. I knew I rarely turned off my laptop
when not using it. The last two were things I had never considered before, so
I wanted to start thinking about them and save some energy in that area.

Turning the heat down is becoming easier now that the weather is warming up.
With this action item on the list, however, I have completely left the heater
off and jumped around (touching the ceiling!) in the morning to warm myself up.

Turning off my laptop at the end of the day has so far been easy to do.

Matching pan to element size is still a bit challenging. Sometimes I choose an
element size too small, which unevenly heats the bottom of a large pan. Finding
and adjusting to the ``right size'' for each pan in our house is taking
a while.

Washing full loads is easy because I have a lot of shirts, and I change every
day. It will become easier as summer approaches and I generate more laundry.

\subsection*{Post-assessment}

I was successful on all five action items, especially the first three easier
items. It is easy for me to leave every place I visit as if it was uninhabited
(which it technically is after I depart); this usually means everything is off,
off, and off.

I am still working on matching pan sizes. I have paid particular attention to
heat escaping past the sides of pans that are too small for their elements, and
I can imagine the energy waste that results. I wish I had a heat gun so I could
see it myself!

Washing full loads has so far been successful, though I have only had two loads
to wash, which is a rather small sample size.

These habits did not affect my daily routine very much, and I cannot imagine
they will hurt my productivity at all in the long run once I relearn my pan
sizes. Tuning up my car was enjoyable just for its own sake as well as for my
knowing that my car was as efficient as I could make it. Knowing the same about
the way I live and conduct my activities feels good, too.

\subsection*{Survey Completion Form}

I signed up for Energize Corvallis too late and do not have a form.

\end{document}
